%==============================================================================
% Dante Mazza — Resume
% ATS-friendly, single-column, selectable text. Build with: ./build.sh
%==============================================================================
\documentclass[letterpaper,10pt]{article}

\usepackage[margin=0.45in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
\definecolor{linknavy}{HTML}{1A5276}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=linknavy, linkcolor=linknavy}
\usepackage{parskip}
\setlength{\parskip}{2pt}

\pagestyle{empty}

% --- Section headings: simple, uppercase, ruled (ATS reads these as headers) ---
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{5pt}

% --- Helper commands ----------------------------------------------------------
% Single-role entry: company + location on one line, title + dates below
\newcommand{\role}[4]{%
  \noindent\textbf{#1}\hfill #2\\[1pt]%
  \textit{#3}\hfill \textit{#4}\par%
}

% Company header (for an employer with multiple stacked roles)
\newcommand{\company}[2]{%
  \noindent\textbf{#1}\hfill #2\par%
}

% Role line under a \company (title + dates)
\newcommand{\subrole}[2]{%
  \noindent\textit{#1}\hfill \textit{#2}\par%
}

% Compact bullet list
\newenvironment{bullets}{%
  \begin{itemize}[leftmargin=1.5em,topsep=2pt,itemsep=1pt,parsep=0pt]%
}{\end{itemize}}

\setlength{\parindent}{0pt}

%==============================================================================
\begin{document}

% ----- Header -----------------------------------------------------------------
\begin{center}
  {\fontsize{32}{34}\selectfont \textbf{Dante Mazza}}\\[3pt]
  {\small 425-542-4364 $\cdot$ \href{mailto:dantemazza1@gmail.com}{dantemazza1@gmail.com} $\cdot$ \href{https://dantemazza.com}{dantemazza.com}\\[1pt]
  \href{https://github.com/dantemazza}{github.com/dantemazza} $\cdot$ \href{https://www.linkedin.com/in/dante-mazza}{linkedin.com/in/dante-mazza}}
\end{center}

% ----- Skills -----------------------------------------------------------------
\section{Skills}
\textbf{Languages:} Python, Java, Scala, Kotlin, C, C++, SQL\\
\textbf{Frameworks \& Data:} Spring Boot, Flask, FastAPI, Spark, Hadoop, Delta Lake, Iceberg, Redis, Kafka\\
\textbf{Infrastructure:} AWS (EMR, EC2, RDS, Lambda, Step Functions), Docker, Kubernetes, Terraform, Prometheus, Linux\\
\textbf{Tools:} Git, CI/CD (GitLab, GitHub Actions), Claude Code, MCP

% ----- Experience -------------------------------------------------------------
\section{Experience}

\company{Splunk}{Toronto, Canada}
\subrole{Software Engineer II}{Oct 2024 -- Present}
\begin{bullets}
  \item Developing scalable, performant (50 TB/day) AWS-hosted Kubernetes + Java/Spring microservices with PostgreSQL/RDS, SQS, Prometheus, GitLab CI/CD, and Terraform.
  \item Technical lead on an 8 month+ rearchitecture of a Spark ML security detection platform. Designed the data lake, ETL pipeline with feature store, and CI/CD build process, and ran performance PoCs on Parquet writer configs, Delta/Iceberg, and feature computation on EMR.
  \item Led implementation across 3 engineers and 5 partner teams, improved MTTD 90\% (30 to 3 hours), and shipped 1 month ahead of schedule. Mentored 5+ junior engineers and interns.
\end{bullets}

\subrole{Software Engineer I}{Jul 2023 -- Oct 2024}
\begin{bullets}
  \item Built and maintained Spark/Scala batch pipelines using Delta Lake on S3, AWS EMR, and Step Functions to process 1PB+ of logs (VPN, Windows, cloud storage), detecting anomalies across 30M+ users and devices daily.
  \item Designed and implemented an E2E ML model testing framework (Python, AWS, GitLab CI/CD) and advocated for its adoption, cutting testing and deployment time 98\%, from weeks to hours.
  \item Cut team AWS costs 30\% (\$150K/year) by optimizing Spark/Scala ETL pipelines (Glue, Kinesis, Delta Lake) and downstream Spark ML jobs on EMR through performance tuning and code optimization.
\end{bullets}

\subrole{Software Engineer Intern}{Jan 2022 -- Apr 2022}
\begin{bullets}
  \item Prototyped multi-tenant Spark job execution with AWS (EMR, IAM, STS, Step Functions, Lambda), Terraform, Python, Docker, and Java/Spring. Automated tenant provisioning with shell + GitLab/internal APIs, saving 6 hours of onboarding per customer.
\end{bullets}

\vspace{3pt}
\role{Amazon Web Services (Keyspaces)}{Bellevue, WA}{Software Development Engineer Intern}{Aug 2022 -- Dec 2022}
\begin{bullets}
  \item Authored a transactional query service in Kotlin using internal AWS services for a managed Cassandra product. Researched open-source Cassandra batch-query functionality and designed for parity.
\end{bullets}

\vspace{3pt}
\role{Wisedocs}{Toronto, Canada}{Machine Learning Engineer}{May 2020 -- Sep 2021}
\begin{bullets}
  \item Implemented and optimized ML models (CNNs with TensorFlow/Keras, NLP with Hugging Face, k-means with scikit-learn) for a 2x accuracy improvement. Built Python document clustering that cut prediction time 85\%, and a pre-serialized Keras batch-training method that cut training time 90\%.
\end{bullets}

% ----- Projects ---------------------------------------------------------------
\section{Projects}

\role{Shipsolver}{\href{https://shipsolver.com}{shipsolver.com}}{Sole maintainer of a freight-forwarding B2B suite}{Oct 2025 -- Present}
\begin{bullets}
  \item Building and operating a multi-tenant backoffice platform (2 active customers): automated invoice generation, payroll and driver-compliance management, and user governance. Built with Python/FastAPI, GitHub Actions CI/CD, and AWS (RDS, EC2). Custom Claude Code worktree harness enables parallel local development and rapid feature work.
\end{bullets}

\vspace{3pt}
\role{Tricks \& Trumps}{\href{https://tricksandtrumps.com}{tricksandtrumps.com}}{Real-time multiplayer rubber bridge}{Jan 2024 -- Present}
\begin{bullets}
  \item Built a real-time multiplayer web app for rubber bridge focused on competitive play and an intuitive scorekeeping interface.
\end{bullets}

% ----- Education --------------------------------------------------------------
\section{Education}
\noindent\textbf{University of Waterloo}, BASc in Computer Engineering \hfill Sep 2018 -- May 2023\\
Dean's Honour List (first year). Relevant coursework: Distributed Systems, Compilers, Operating Systems, Networks.

\end{document}
